Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-22 xrb2/paper.tex
Fixed Yuri's institution
Removed streamlines discussion

\author[0000-0002-6447-3603]{Y.\ Cavecchi}
\affiliation{Universidad Nacional Aut\'{o}noma M\'{e}xico, Instituto de Astronom\'{i}a, Ciudad Universitaria, CDMX 04510, Mexico}

@@

\MarginPar{NF: Each of the figures referenced in this paragraph contributes to the idea that we are seeing burning/energy generation from fluid undergoing vortical motion/fuel being entrained around the flame edge... I just think the logical flow of the sentences could be a bit better.}
Burning in the {\tt F500} and {\tt F1000} runs is concentrated in a hot, dense region with circular 
motion. {\color{blue} We visualize the velocity field in the burning region for the {\tt F500} run in Figure~\ref{fig:streamlines}, colored by temperature. Velocities near the bottom edge of the high temperature/high density region (white) tend to have a significant $+z$ component. This boundary most likely corresponds to the leading edge of the flame, where colder fuel undergoes vortical motion and becomes entrained into the burning front.} In Figure~\ref{fig:urho}, which compares the horizontal $r$-velocity $u$, density $\rho$ and the 
nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the {\tt F250}, {\tt F500}, and {\tt F1000} 
runs, most of the burning for each of the simulations occurs in a high density region $\rho > 3 
\times 10^5 {\rm g\,cm^{-3}}$. The fluid in this dense, high energy generation region undergoes 
vortical motion, shown in the Figure~\ref{fig:uv} phase plots comparing $u$, vertical z-velocity $v$ and $\dot{e}_{\rm 
nuc}$. {\color{blue} This agrees with the velocity streamlines shown in Figure~\ref{fig:streamlines}.}
This feature is not developed in the $250~\mathrm{Hz}$ flame in Figure~\ref{fig:uv} {\color{blue} (left panel)}; it could potentially develop 
at later times (past the point at which we terminated our simulation), or the flame could just 
fizzle out and fail to ignite entirely.

\begin{figure}
  \plotone{streamlines_500Hz_temp.pdf}
  \caption{\label{fig:streamlines}Streamlines showing the velocity field at time $t = 
  100~\mathrm{ms}$ for the {\tt F500} run. Streamline segments are colored by transverse velocity 
  (yellower implies faster flow), and segments with transverse velocity $v < 2 \times 
  10^6~\mathrm{cm/s}$ are scrubbed out. Note that the plot has been stretched vertically to 
  better show the streamlines -- the aspect ratio is not the aspect ratio of the simulation 
  domain.}
\end{figure}

>>>>

\author[0000-0002-6447-3603]{Y.\ Cavecchi}
\affiliation{Universidad Nacional Aut\'{o}noma de M\'{e}xico, Instituto de Astronom\'{i}a, Ciudad Universitaria, CDMX 04510, Mexico}

@@

Burning in the {\tt F500} and {\tt F1000} runs is concentrated in a dense region with circular 
motion. In Figure~\ref{fig:urho}, which compares the horizontal $r$-velocity $u$, density $\rho$ and the 
nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the {\tt F250}, {\tt F500}, and {\tt F1000} 
runs, most of the burning for each of the simulations occurs in a high density region $\rho > 3 
\times 10^5 {\rm g\,cm^{-3}}$. The fluid in this dense, high energy generation region undergoes 
vortical motion, shown in the Figure~\ref{fig:uv} phase plots comparing $u$, vertical z-velocity $v$ and $\dot{e}_{\rm 
nuc}$. This most likely corresponds to the leading edge of the flame where fresh fuel is being entrained. \MarginPar{not sure if we should keep this sentence about entrainment...}
This feature is not developed in the $250~\mathrm{Hz}$ flame in Figure~\ref{fig:uv} {\color{blue} (left panel)}; it could potentially develop 
at later times (past the point at which we terminated our simulation), or the flame could just 
fizzle out and fail to ignite entirely.
